---
title: "COVID-19 Burden on Ontario Healthcare Resources"
author: "Carson Fong"
date: "April 10, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

# Viewable here: https://rpubs.com/carsonfong/covid_ontario

# Import data from Ontario's open dataset
on_daily_cases <- read_csv("https://data.ontario.ca/dataset/f4f86e54-872d-43f8-8a86-3892fd3cb5e6/resource/ed270bb8-340b-41f9-a7c6-e8ef587e6d11/download/covidtesting.csv")

# Take subset of data starting Apr 2, when the dataset first starts reporting this metric
ICU_vent_data <- on_daily_cases %>%
  select(`Reported Date`,`Number of patients in ICU on a ventilator with COVID-19`) %>%
  filter(`Reported Date` >= "2020-04-02")



```

## Daily Count of COVID-19 Patients in Ontario ICUs with Ventilators

This is a simple graph that pulls the publicly available data on the number of patients in ICUs on a ventilator in Ontario.

As described by the Ontario Open Data Team, this includes COVID-19 patients in levels 2 and 3 flex, neonatal, pediatric, and adult ICU beds. Numbers reflect the previous day's value, counted at 11:59PM. Data was available as of the reporting date of April 2, 2020.

Source: https://data.ontario.ca/dataset/status-of-covid-19-cases-in-ontario

```{r cars, echo=FALSE}

# Plot
plot_daily_icu_vent <- ggplot(ICU_vent_data, aes(x=`Reported Date`, y=`Number of patients in ICU on a ventilator with COVID-19`)) +
  geom_line() +
  expand_limits(y=0)

plot_daily_icu_vent

```


